CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

```{r exit, cache=FALSE, eval=FALSE}
knitr::knit_exit()
```

@@

## Module enrichment
```{r top.enrich.Dx_sex}
df_module = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Dx_Sex)

>>>>

@@

## Module enrichment
```{r top.enrich.Dx_Sex}
df_module = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Dx_Sex)
